---
title: "Visualizing Conditional Distributions using ggplot2"
---

# Exercise 3

Load packages and the data set:

```{r echo = FALSE, warning = FALSE, message = FALSE}
library("ggplot2")
library("dplyr")
library("stringr")
data("CHFLS", package = "HSAUR2")
```

# Histograms on facets

Plot histograms by groups on facets, setting the binwith according to the range of the data. Set the scales for each plot freely.

```{r}
CHFLS %>%
  ggplot(aes(x = R_income)) + 
  geom_histogram(fill = "red", binwidth = diff(range(CHFLS$R_income))/50) + 
  facet_wrap(~ R_edu, scales = "free") + 
  theme_bw()
```

# Barplots by groups

Stacked barplots

```{r}
CHFLS %>%
  ggplot(aes(x = R_happy, fill = R_edu)) + geom_bar() + 
  theme_bw()
```

Barplots on facets wrapping the text on the x axis using _stringr_ package.

```{r}
CHFLS %>%
  ggplot(aes(x = R_happy)) + 
  facet_wrap(~ R_edu) + 
  geom_bar(fill = "red") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 6)) +
  theme_bw()
```

# Jittered dotplot

Convert continuous data to discrete with _cut_. Plot data points by groups as _jittered dotplot_, and add boxes for median and quartiles.

```{r}
CHFLS %>%
  mutate(R_income_group = cut(R_income, c(0, 250, 500, 1000, 10001), right = FALSE)) %>%
  ggplot(aes(x = R_income_group, y = R_age)) + 
  geom_jitter(position = position_jitter(0.25), alpha = 0.4) +
  stat_summary(fun.y = median, fun.ymin = function(x) quantile(x, 0.25), 
               fun.ymax = function(x) quantile(x, 0.75),
               geom = "crossbar", width = 0.5, col = "red") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  theme_bw()
```


## Grouped scatterplots

Draw a single scatterplot, groups as different colors. Draw regression lines without confidence intervals for a better visibility.

```{r}
CHFLS %>%
  ggplot(aes(x = R_income, y = A_income, color = A_edu)) + 
  geom_point() +
  geom_smooth(method = lm, se = FALSE) +
  theme_bw()
```

Draw scatterplots by groups on facets, set plot scales independently, add regression lines with confidence intervals.

```{r}
CHFLS %>%
  ggplot(aes(x = R_income, y = A_income)) + 
  geom_point(color = "red") + facet_wrap(~ A_edu, scales = "free") +
  geom_smooth(method = lm, color = "black") +
  theme_bw()
```

